### 2023-12-11 Notes/optest_update.tex
I understand why the linear model is not optimal in the non-linear case. The weights are higher for smaller estimates with a smaller variance.

\begin{tabular}{lrrr}
  \toprule
  Estimator & $\beta_0(\delta, c_0)$ & $\beta_1(\delta, c_1)$ & Implemented \\
  \midrule
  $\hat \theta_{prop}$ & $\left(1 - \frac{(\delta_{10} + \delta_{11})}{(\pi_{10} + \pi_{11})} - 
  \frac{(\delta_{01} + \delta_{11})}{(\pi_{01} + \pi_{11})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $\left(\frac{\delta_{10} + \delta_{11}}{\pi_{10} + \pi_{11}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta^{ind}_{prop}$ & $\left(1 - \frac{(\delta_{10})}{(\pi_{10})} - 
  \frac{(\delta_{01})}{(\pi_{01})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $\left(\frac{\delta_{10}}{\pi_{10}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta_{c}$ & $c_0\left(1 - \frac{(\delta_{10} + \delta_{11})}{(\pi_{10} + \pi_{11})} - 
  \frac{(\delta_{01} + \delta_{11})}{(\pi_{01} + \pi_{11})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $c_1\left(\frac{\delta_{10} + \delta_{11}}{\pi_{10} + \pi_{11}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \\
  $\hat \theta_{c, ind}$ & $c_0\left(1 - \frac{(\delta_{10})}{(\pi_{10})} - 
  \frac{(\delta_{01})}{(\pi_{01})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $c_1\left(\frac{\delta_{10}}{\pi_{10}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta_{\delta}$ & $c_0\left(\frac{\delta_{11}}{\pi_{11}} - \frac{\delta_{00}}{\pi_{00}}\right)$ &
  $c_1\left(\frac{\delta_{11}}{\pi_{11}} - \frac{\delta_{10}}{\pi_{10}}\right)$ & \checkmark \\
  \bottomrule
\end{tabular}

@@

\begin{table}[ht!]
\caption{The true value of $\theta$ is 5. $\rho = 0.5$. The test statistic and 
p-value are from a one-sample t-test to see if the estimator is biased.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Algorithm & Bias & SD & Tstat & Pval\\
\midrule
Oracle & 0.001 & 0.044 & 1.546 & 0.061\\
CC & 0.002 & 0.058 & 1.549 & 0.061\\
IPW & 0.006 & 0.210 & 1.504 & 0.066\\
$\hat \theta_{prop}$ & 0.002 & 0.051 & 1.911 & 0.028\\
$\hat \theta_{prop}^{ind}$ & 0.002 & 0.091 & 0.983 & 0.163\\
$\hat \theta_{c, ind}$ & 0.001 & 0.074 & 0.784 & 0.216\\
$\hat \theta_{\delta}$ & 0.002 & 0.051 & 1.964 & 0.025\\
\bottomrule
\end{tabular}
\end{table}

The main takeaway from this simulation study is that $\hat \theta_\delta$
and $\hat\theta_{prop}$ have the smallest standard deviation among the 
non-oracle estimators.

\subsection*{Simulation 2}
We now test a second simulation study. The setup of this simulation study 
is the same as the previous simulation. The only difference is that we 
are interested in estimating $\theta = E[Y_1^2 Y_2]$. In other words, now 
we have $g(Z) = Y_1^2 Y_2$.

\begin{table}[ht!]
  \caption{The true value of $E[g(Z)]$ is 10. $\rho = 0.5$. The test statistic and 
p-value are from a one-sample t-test to see if the estimator is biased.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Algorithm & Bias & SD & Tstat & Pval\\
\midrule
Oracle & 0.007 & 0.529 & 0.741 & 0.229\\
CC & 0.023 & 0.824 & 1.518 & 0.065\\
IPW & 0.031 & 0.915 & 1.846 & 0.032\\
$\hat \theta_{prop}$ & 0.011 & 0.635 & 0.912 & 0.181\\
$\hat \theta_{c, ind}$ & 0.013 & 0.662 & 1.060 & 0.145\\
$\hat \theta_{\delta}$ & 0.011 & 0.636 & 0.983 & 0.163\\
\bottomrule
\end{tabular}
\end{table}

Like the first simulation, $\hat \theta_{prop}$ and $\hat \theta_{\delta}$ 
performed the best.

>>>>

\begin{tabular}{lrrr}
  \toprule
  Estimator & $\beta_0(\delta, c_0)$ & $\beta_1(\delta, c_1)$ & Implemented \\
  \midrule
  $\hat \theta_{prop}$ & $\left(1 - \frac{(\delta_{10} + \delta_{11})}{(\pi_{10} + \pi_{11})} - 
  \frac{(\delta_{01} + \delta_{11})}{(\pi_{01} + \pi_{11})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $\left(\frac{\delta_{10} + \delta_{11}}{\pi_{10} + \pi_{11}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta^{ind}_{prop}$ & $\left(1 - \frac{(\delta_{10})}{(\pi_{10})} - 
  \frac{(\delta_{01})}{(\pi_{01})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $\left(\frac{\delta_{10}}{\pi_{10}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta_{c}$ & $c_0\left(1 - \frac{(\delta_{10} + \delta_{11})}{(\pi_{10} + \pi_{11})} - 
  \frac{(\delta_{01} + \delta_{11})}{(\pi_{01} + \pi_{11})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $c_1\left(\frac{\delta_{10} + \delta_{11}}{\pi_{10} + \pi_{11}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta_{c, ind}$ & $c_0\left(1 - \frac{(\delta_{10})}{(\pi_{10})} - 
  \frac{(\delta_{01})}{(\pi_{01})} + \frac{\delta_{11}}{\pi_{11}}\right)$ &
  $c_1\left(\frac{\delta_{10}}{\pi_{10}} - \frac{\delta_{11}}{\pi_{11}}\right)$ & \checkmark \\
  $\hat \theta_{\delta}$ & $c_0\left(\frac{\delta_{11}}{\pi_{11}} - \frac{\delta_{00}}{\pi_{00}}\right)$ &
  $c_1\left(\frac{\delta_{11}}{\pi_{11}} - \frac{\delta_{10}}{\pi_{10}}\right)$ & \checkmark \\
  \bottomrule
\end{tabular}

@@

\begin{table}[ht!]
\caption{The true value of $\theta$ is 5. $\rho = 0.5$. The test statistic and 
p-value are from a one-sample t-test to see if the estimator is biased.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Algorithm & Bias & SD & Tstat & Pval\\
\midrule
Oracle & 0.001 & 0.044 & 1.546 & 0.061\\
CC & 0.002 & 0.058 & 1.549 & 0.061\\
IPW & 0.006 & 0.210 & 1.504 & 0.066\\
$\hat \theta_{prop}$ & 0.002 & 0.051 & 1.911 & 0.028\\
$\hat \theta_{c}$ & 0.002 & 0.051 & 1.920 & 0.027\\
$\hat \theta_{prop}^{ind}$ & 0.002 & 0.091 & 0.983 & 0.163\\
$\hat \theta_{c, ind}$ & 0.001 & 0.074 & 0.784 & 0.216\\
$\hat \theta_{\delta}$ & 0.002 & 0.051 & 1.964 & 0.025\\
\bottomrule
\end{tabular}
\end{table}

The main takeaway from this simulation study is that $\hat \theta_\delta$,
$\hat \theta_c$
and $\hat\theta_{prop}$ have the smallest standard deviation among the 
non-oracle estimators. In fact $\hat \theta_c$ and $\hat \theta_{prop}$ are 
virtually identical because the optimal values of $c$ in $\hat \theta_c$ 
are $(c_0, c_1, c_2)' \approx (1, 1, 1)'$.

\subsection*{Simulation 2}

We now test a second simulation study. The setup of this simulation study 
is the same as the previous simulation. The only difference is that we 
are interested in estimating $\theta = E[Y_1^2 Y_2]$. In other words, now 
we have $g(Z) = Y_1^2 Y_2$.

\begin{table}[ht!]
  \caption{The true value of $E[g(Z)]$ is 10. $\rho = 0.5$. The test statistic and 
p-value are from a one-sample t-test to see if the estimator is biased.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Algorithm & Bias & SD & Tstat & Pval\\
\midrule
Oracle & 0.007 & 0.529 & 0.741 & 0.229\\
CC & 0.023 & 0.824 & 1.518 & 0.065\\
IPW & 0.031 & 0.915 & 1.846 & 0.032\\
$\hat \theta_{prop}$ & 0.011 & 0.635 & 0.912 & 0.181\\
$\hat \theta_{c}$ & 0.012 & 0.632 & 1.010 & 0.156\\
$\hat \theta_{c, ind}$ & 0.013 & 0.662 & 1.060 & 0.145\\
$\hat \theta_{\delta}$ & 0.011 & 0.636 & 0.983 & 0.163\\
\bottomrule
\end{tabular}
\end{table}

Like the first simulation, $\hat \theta_{prop}$, $\hat \theta_c$
and $\hat \theta_{\delta}$ performed the best.
